---
title: "Report on USA gun murder"
author: "Kaycee"
date: "19 June 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introcution

This is a report on 2010 gun murder rates obtained from FBI reports. The original data wa obtained from [this wikipedia page]
(https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state).

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

We are going to use the following library:

```{r loading-libs,message=FALSE}
library(tidyverse,ggthemes)
```

and load the data we arleady wrangled:

```{r}
load("rda/murders.rda")
```

## Murder rate by state 

We note the large state tp state variability by generating a barplot showing the murder rate by state:

```{r murder-rate-by-state,echo=FALSE}
library(ggthemes)
r<-murders %>% 
  summarise(rate=sum(total)/sum(population)*10^6) %>% .$rate
murders %>% ggplot(aes(population/10^6,total,label=abb))+
  geom_point(aes(col=region),size=3)+
  geom_text(nudge_x = 0.05)+
  geom_abline(intercept = log10(r),lty=2,col="darkgrey")+
  scale_x_log10()+
  scale_y_log10()+
  labs(title="USA gun murder rate in 2010", xlab="Population in millions(log sclae)",
       ylab="Total number of murders(log scale)", col="Region")+
  theme_economist()


